smdi: An R package to perform structural missing data investigations on partially observed confounders in real-world databases

### 2023-08-01 manuscript/manuscript.qmd
introduced headings according to general instructions page

```{r setup}
#| label: setup
#| include: false
library(cowplot)
library(here)
library(tidyverse)
library(readxl)
library(gt)
library(gtsummary)
library(flextable)
library(officer)
library(captioner)
library(smdi)

@@

# Background

@@

@@

>>>>

```{r setup}
#| label: setup
#| include: false
library(cowplot)
library(here)
library(tidyverse)
library(readxl)
library(gt)
library(gtsummary)
library(flextable)
library(officer)
library(captioner)

@@

# Background and Significance

@@

# Objective

@@

## **Package details and installation instructions**

...
